MNRAS \LaTeXe\ template -- title goes here

### 2017-10-17 Paper/paper.tex
changes

\section{Illustris Simulation}
Illustris-1, also known simply as Illustris, is a highly resolved
cosmological simulation which reproduces large-scale statistical
features of the Universe, such as the galaxy population of massive
clusters, as well as small-scale properties such as the morphology of
galaxies and detailed values for their stellar and gas content.\\

@@

The evolution in time was performed with the hydrodynamic code AREPO
\cite{arepo}, which combines a moving Voronoi tessellation with the
finite volume approach. Included in the evolution algorithm, there are
galaxy formation models which account for the evolution of stars and
SMBHs. Specifically, the physics followed by this model includes
energetic feedback from supermassive black holes and supernovae, as
well as stellar evolution and chemical enrichment. This level of
detail in Illustris is advantageous for the analysis of the effect of
the environment  in galactic barionic properties and is hard to find
among other simulations, i.e. post-processed runs with semi-analytical
models which do not directly simulate baryons.(Expand) Describe Arepo
a little bit more\\

The output of this simultaion consists of 136 snapshots where 61 of
them were taken at $z < 3$ spaced with a cosmological scale factor
$\Delta a \approx 0.02$, while the remaining 75 were taken at $z > 3$
with spacing $\Delta a \approx 0.01$. Each snapshot was post-processed
with a modified version of FOF \cite{FOF} to identify DM haloes with
more than 32 particles using a linking length of 0.2 times the mean
particle separation each of which is analyzed with the SUBFIND
algorithm \cite{subfind} to generate, at z=0, 7,713,601 halos (FOF)
and 4,366,546 (sub)halo catalogues with their respective
characterization properties. \\

@@

The principal purpose of this work is to verify if the results
obtained observationally by Jones et al. \cite{jones1} are supported
by a similar analysis in the cosmological simulation Illustris. For
this purpose, we want to adaptate the observational method as closely
as posible for it to work on computational data.\\

\subsection{The $3^{rd}$ nearest neighbor method}

The principal method used in Jones et al. \cite{jones1} analyses the
dependence of the Schechter parameters on the cosmological
environment. To obtain a quantification of said cosmological
environment, they calculated for each galaxy in the studied survey the
projected distance in the sky to the third nearest neighbor,
filtrating candidate neighbors by its radial velocity relative to the
reference galaxy. According to Hubble's law, this effectively
restricts the candidate galaxies to a smaller radial range, reducing
apparent closer galaxies arising from the projection method. The
radial relative velocity cut was chosen to be $450km/s$. Furthermore,
a photometrics pre-selection was performed, selecting galaxies whose
r-filter magnitude was above $-19$ (VERIFY).\\

Once quantified the environment with the distance to the 3rd nearest
neighbor definition for each galaxy in their post-selected survey they
divided the group in four quartiles according this quantity. For each
quartile, the respective HIMF was calculated, and with this, a
Schechter fit was obtained. The analysis was specifically performed
over the Schechter parameters of the Knee-mass and the faint-end
slope. \\

In dark matter cosmological simulations, access to the information is
istantaneous and at no cost. However, as we want to replicate as
closely as possible the method effectuated by Jones et. al
\cite{jones1}, we also calculate the projected distance in the
simulation and take the same projected velocity cut according to a
specified point of view. Even when we could easily calculate the
distance to the third nearest neighbor we take into account these
observational simplifications, to make our study as comparable as
possible to that of Jones et al. \cite{jones1}.\\

However, as Illustris is a cosmological simulation, it is subject to numerical resolution biases, being the most important, the mass resolution biases. Each mass considered here is subject directly or indirectly to a mass resolution, and the effect it causes is specially evident in the produced mass functions. We used Illustris-3, which is a less resoluted copy of Illustris-1, to verify that the effect on the mass functions is indeed caused by mass resolution. Taking this into account, mass functions are heavily affected for masses below a certain cut and for this reason, only galaxies above said cut are considered in this study. This mass cut has no aparent systematical way to be calculated and therefore, we performed the cut having into account the performance of the respective Schechter fit.\\

Mass resolution reduces the size of the sample galaxies and this
complicates the process of photometrics pre-selection. This selection
significatively reduces the size of the galaxy set which is already
smaller than normal due to the resolution cut. This made impossible a
Schechter fit to the obtained mass functions given that the associated
logarithmic errors became extremely large. For this reason, we omit
the photometrics pre-selection which is the only feature that our
analysis misses with respect to the one from \cite{jones1}.\\

\subsection{The cosmic web method}
To complement the analysis performed with the third nearest neighbor
method for the classification of environments, we chose a
complementary method of completely different nature to verify even
more the results from Jones et al.. The method chosen here was the one
developed by Forero et al. \cite{forero1}, which uses the Hessian of
the gravitational potential obtained from the DM field to classify
galaxies into (conveniently) four morphological environments.\\

@@

% Quartiles gas
\begin{figure}
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\columnwidth]{./pics/quartilesGas.png}
    \caption{\textbf{Upper side}: Schechter fits of each gas mass
      function for each environmental quartile using the 3rd nearest
      neighbor definition.\textbf{Down side}: Knee-mass $m_\ast$ and
      the faint end slope $\alpha$ values obtained from the Schechter
      fits for each curve shown above.} 
    \label{fig:quartilesGas}
\end{figure}

@@

% Quartiles DM
\begin{figure}
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\columnwidth]{./pics/quartilesDM.png}
    \caption{\textbf{Upper side}: Schechter fits of each DM mass
      function for each environmental quartile using the 3rd nearest
      neighbor definition.\textbf{Down side}: Knee-mass $m_\ast$ and
      the faint end slope $\alpha$ values obtained from the Schechter
      fits for each curve shown above.} 
    \label{fig:quartilesDM}
\end{figure}

% Tweb DM
\begin{figure}
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\columnwidth]{./pics/T-Web_DM.png}
    \caption{\textbf{Upper side}: Schechter fits of each DM mass
      function for each morphological environment characterized by the
      T-Web algorithm proposed by Forero et al.\textbf{Down side}:
      Knee-mass $m_\ast$ and the faint end slope $\alpha$ values
      obtained from the Schechter fits for each curve shown above.} 
    \label{fig:TwebDM}
\end{figure}

% Quartiles Stellar
\begin{figure}
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\columnwidth]{./pics/quartilesSellar.png}
    \caption{\textbf{Upper side}: Schechter fits of each stellar mass
      function for each environmental quartile using the 3rd nearest
      neighbor definition.\textbf{Down side}: Knee-mass $m_\ast$ and
      the faint end slope $\alpha$ values obtained from the Schechter
      fits for each curve shown above.} 
    \label{fig:quartilesStellar}
\end{figure}

% Tweb Stellar
\begin{figure}
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\columnwidth]{./pics/T-Web_Stellar.png}
    \caption{\textbf{Upper side}: Schechter fits of each stellar mass
      function for each morphological environment characterized by the
      T-Web algorithm proposed by Forero et al.\textbf{Down side}:
      Knee-mass $m_\ast$ and the faint end slope $\alpha$ values
      obtained from the Schechter fits for each curve shown above.} 
    \label{fig:TwebStellar}
\end{figure}

% Quartiles BH
\begin{figure}
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\columnwidth]{./pics/quartilesBH.png}
    \caption{\textbf{Upper side}: Schechter fits of each BH mass
      function for each environmental quartile using the 3rd nearest
      neighbor definition.\textbf{Down side}: Knee-mass $m_\ast$ and
      the faint end slope $\alpha$ values obtained from the Schechter
      fits for each curve shown above.} 
    \label{fig:quartilesBH}
\end{figure}

% Tweb BH
\begin{figure}
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\columnwidth]{./pics/T-Web_BH.png}
    \caption{\textbf{Upper side}: Schechter fits of each BH mass
      function for each morphological environment characterized by the
      T-Web algorithm proposed by Forero et al.\textbf{Down side}:
      Knee-mass $m_\ast$ and the faint end slope $\alpha$ values
      obtained from the Schechter fits for each curve shown above.} 
    \label{fig:TwebBH}
\end{figure}

>>>>

\section{Illustris Simulation}
Illustris-1, also known simply as Illustris, is a highly resolved
cosmological simulation. It reproduces large-scale statistical
features of the Universe, such as the galaxy population of massive
clusters, as well as small-scale properties such as the morphology of
galaxies and detailed values for their stellar and gas content.\\

@@

The evolution in time was performed with the hydrodynamic code AREPO
\cite{arepo}, which combines a moving Voronoi tessellation with the
finite volume approach. Included in the evolution algorithm, there are
galaxy formation models which account for the evolution of stars and
SMBHs. Specifically, the physics followed by this model includes
energetic feedback from supermassive black holes and supernovae, as
well as stellar evolution and chemical enrichment. This level of
detail in Illustris is advantageous for the analysis of the effect of
the environment in barionic properties of galaxies. This level of resolution is hard to find
among other simulations, i.e. post-processed runs with semi-analytical
models which do not directly simulate baryons.(Expand) Describe Arepo more\\

The output of this simultaion consists of 136 snapshots. 61 of
them were taken at $z < 3$ spaced with a cosmological scale factor
$\Delta a \approx 0.02$. The remaining 75 were taken at $z > 3$
with spacing $\Delta a \approx 0.01$. Each snapshot was post-processed
with a modified version of FOF \cite{FOF} to identify DM haloes with
more than 32 particles using a linking length of 0.2 times the mean
particle separation. Each output group from the 7,713,601 post-processed halos (FOF) is analyzed with the SUBFIND
algorithm \cite{subfind} to generate, at z=0,
and 4,366,546 (sub)halo catalogues with their respective
characterization properties. \\

@@

The principal purpose of this work is to verify if the results
obtained observationally by Jones et al. \cite{jones1} are supported
by a similar analysis in the cosmological simulation Illustris. Specifically, we focus on the (small-scale) environment definition of the $3^{rd}$ nearest neighbor, which we want to adapt as closely as possible to our computational application.\\

\subsection{The $3^{rd}$ nearest neighbor definition of environment}

Jones et al. \cite{jones1} analyses the
dependence of the Schechter parameters on the cosmological
environment. To obtain a quantification of said cosmological
environment, they calculated for each galaxy in the studied survey the
projected distance in the sky to the third nearest neighbor,
filtrating candidate neighbors by their radial velocity relative to the
reference galaxy. According to Hubble's law, this effectively
restricts the candidate galaxies to a smaller radial range, reducing
apparent closer galaxies arising from the projection method. The
radial relative velocity cut was chosen to be $450km/s$. In addition to this,
a photometrics pre-selection was performed, selecting galaxies whose
r-filter magnitude was above $-19$ (VERIFY).\\

Once quantified the environment with the distance to the 3rd nearest
neighbor definition they divided the group in four quartiles according this quantity. For each
quartile, the respective HIMF was calculated, and with this, a
Schechter fit was obtained. The analysis was specifically performed
over the Schechter parameters of the Knee-mass and the faint-end
slope. (Some observational adjustments for the Schechter functions were performed)  \\

As we want to replicate as closely as possible the method effectuated by Jones et. al
\cite{jones1}, we use the same specifications to calculare the environment.
 We perform the analysis of the Schechter functions to gas, DM, stellar and BH mass functions.
 However, we do not perform it directly on HIMFs because this would require some extense calculations.
  We take the gas mass function as a first approximation.
 As Illustris is a cosmological simulation, it is subject to resolution biases.
The most important bias in this study is related to the minimum mass of discrete elements in the simulation. 
Each mass considered here is subject directly or indirectly this resolution restriction, and the effect it causes is specially evident in the produced mass functions. 
We used Illustris-2,3, which are less resoluted copies of Illustris-1, to show this effect on the mass functions \fig{resolution effects}. 
Taking this into account, mass functions are heavily affected for masses below a certain cut and for this reason, only galaxies above said cut are considered in this study. This mass cut has no aparent systematical way to be calculated and therefore, we performed the cut having into account the performance of the respective Schechter fit.\\

\subsection{The cosmic web method}
To complement and verify the analysis performed with the third nearest neighbor
method, we chose a complementary method of completely different nature. 
The chosen method was developed by Forero et al. \cite{forero1}. 
It uses the Hessian \ref{eq:hessian} of
the gravitational potential obtained from the DM density field to classify
galaxies into four morphological environments.\\

\begin{equation}
E =  mc^2
\label{eq:hessian}
\end{equation}

Specifically, we diagonalize the Hessian matrix obtaining three eigenvalues. 
These eigenvalues determine the concavity of the gravitational potential on the principal axes, at each point. We use these eigenvalues to interpret the tendence of mass to cluster with reference with some given threshold $\lambda$. 
Eigenvalues bigger than $\lambda$ are interpreted as a local tendence of mass to expand? in the respective eigenaxes, and viceversa. 
With this characterization, clusters, sheets, fillaments and voids can be defined with the number of axes above $\lambda$.
Forero et. al. found in \cite{forero1} that the critical value that better reproduces the correct morphological pulations was $\lambda = 0.2$. \\

With these specifications, we could obtain mass functions for galaxies belonging to clusters, fillaments and sheets. The amount of galaxies belonging to voids was strongly affected by the mentioned mass cuts and could not produce reasonable mass functions to analyze.

@@

% Quartiles gas
\begin{figure}
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\columnwidth]{./pics/quartilesGas.png}
    \caption{\textbf{Upper side}: Schechter fits of each gas mass
      function for each environmental quartile (tendence) using the 3rd nearest
      neighbor definition.\textbf{Down side}: Knee-mass $m_\ast$ and
      the faint end slope $\alpha$ values obtained from the Schechter
      fits for each curve shown above.} 
    \label{fig:quartilesGas}
\end{figure}

@@

% Quartiles DM
\begin{figure}
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\columnwidth]{./pics/quartilesDM.png}
    \caption{Similar to figure \ref{fig:quartilesGas} using DM.} 
    \label{fig:quartilesDM}
\end{figure}

% Tweb DM
\begin{figure}
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\columnwidth]{./pics/T-Web_DM.png}
    \caption{Similar to figure \ref{fig:TwebGas} using DM.} 
    \label{fig:TwebDM}
\end{figure}

% Quartiles Stellar
\begin{figure}
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\columnwidth]{./pics/quartilesSellar.png}
    \caption{Similar to figure \ref{fig:quartilesGas} using stellar mass} 
    \label{fig:quartilesStellar}
\end{figure}

% Tweb Stellar
\begin{figure}
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\columnwidth]{./pics/T-Web_Stellar.png}
    \caption{Similar to figure \ref{fig:TwebGas} using stellar mass} 
    \label{fig:TwebStellar}
\end{figure}

% Quartiles BH
\begin{figure}
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\columnwidth]{./pics/quartilesBH.png}
    \caption{Similar to figure \ref{fig:quartilesGas} using BHs mass.} 
    \label{fig:quartilesBH}
\end{figure}

% Tweb BH
\begin{figure}
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\columnwidth]{./pics/T-Web_BH.png}
    \caption{Similar to figure \ref{fig:TwebGas} using BHs mass.} 
    \label{fig:TwebBH}
\end{figure}
